Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle

### 2022-04-29 reportTII-ArticleHIL.tex
Updated report

      \begin{tikzpicture}[x=1.5cm, y=1.5cm]

@@

The neural network inputs are mapped to the outputs by being assigned a set of weights~\footnote{\url{https://towardsdatascience.com/machine-learning-for-beginners-an-introduction-to-neural-networks-d49f22d238f9}}. 
The approximated neural network signal can be written as:
\begin{align}
  \label{eq:approximatePolicyActorWeights}
    \hat{\mathbf{u}}_{a,k} = \mathbf{W}_a^T\bm{\sigma}(\mathbf{e}_k),
  \end{align}
%
where $\bm{\sigma}:\mathbb{R}^n\to\mathbb{R}^{\bar{n}}$ with $\bar{n} = n(n+1)/2$ and components of weight matrix ${\bf W}_a$ shown in Fig.~\ref{fig:nnActor} are given by %
%
\begin{align*}
  {\bf W}_a = 
  \begin{bmatrix}
    w_a^{1,1} &  w_a^{1,2} & \ldots &w_a^{1,m}\\
    w_a^{2,1} & w_a^{2,2}& \ldots &w_a^{1,m}\\
    \vdots & \ddots & \ldots &\vdots\\
    w_a^{\bar{n},1} & w_a^{\bar{n},2}& \ldots &w_a^{\bar{n},m}
  \end{bmatrix}.
\end{align*}
%
In compact form:
  \begin{align*}
    \bm{\Sigma}\mathbf{W}_a \approx  \mathbf{U}^{[d]},\qquad\text{with}
    % \hat{\mathbf{U}} \approx \mathbf{U}^{[d]}, 
  \end{align*}
  %
  $\mathbb{R}^{\eta\times\bar{n}}\ni \bm{\Sigma} = [\bm{\Sigma}_0,\bm{\Sigma}_1,\ldots,\bm{\Sigma}_{\eta -1}]^T$ with $\bm{\Sigma}_\kappa = \bm{\sigma}^T({\bf e}_{k+\kappa})$ and $\mathbb{R}^{\eta\times m}\ni {\bf U}^{[d]} = [{\bf U}_0,{\bf U}_1,\ldots, {\bf U}_{\eta-1}]^T$ with ${\bf U}_\kappa = \left({\bf u}_{a,\kappa}\right)^T$ for $\kappa = 0,1,\ldots,\eta-1.$

@@

 The neural network is validated by passing another subset of data that was not used for training purposes and comparing the output results of the neural network with the expected output results from the data set. An acceptable neural network model will meet the desired error requirements~\footnote{\url{https://medium.com/autonomous-agents/bayesian-regularization-for-neuralnetworks-2f2d34f03adc}}.

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.48\linewidth}
		\centering    		
    		\includegraphics[angle=270,width=0.9\linewidth]{figs/img/picturesVisitToAStuff/aStuffVisit2Nick}
    		\caption{}
    \end{subfigure}
    \begin{subfigure}[b]{0.48\linewidth}
		\centering    		
    		\includegraphics[angle=270,width=0.9\linewidth]{figs/img/picturesVisitToAStuff/hilMeasurementHannah}
    		\caption{}
    \end{subfigure}
    %\subfigure[b]{\includegraphics[width=0.48\linewidth]{figs/img/picturesVisitToAStuff/aStuffVisit2Nick}}
    %\subfigure[b]{\includegraphics[width=0.48\linewidth]{figs/img/picturesVisitToAStuff/hilMeasurementHannah}}
    \caption{Verifying voltage measurements on the HIL Bench}
    \label{fig:hilMeasuring}
\end{figure}

>>>>

      \begin{tikzpicture}[x=1.25cm, y=1.25cm]

@@

The neural network inputs are mapped to the outputs by being assigned a set of weights~\footnote{\tiny \hsize=0.45\textwidth \url{https://towardsdatascience.com/machine-learning-for-beginners-an-introduction-to-neural-networks-d49f22d238f9}}. 
The approximated neural network signal can be written as:
\begin{align}
  \label{eq:approximatePolicyActorWeights}
    \hat{\mathbf{u}}_{a,k} = \mathbf{W}_a^T\bm{\sigma}(\mathbf{e}_k),
  \end{align}
%
where $\bm{\sigma}:\mathbb{R}^n\to\mathbb{R}^{\bar{n}}$ with $\bar{n} = n(n+1)/2$ and components of weight matrix ${\bf W}_a$ shown in Fig.~\ref{fig:nnActor} are given by %
%
\begin{align*}
  {\bf W}_a = 
  \begin{bmatrix}
    w_a^{1,1} &  w_a^{1,2} & \ldots &w_a^{1,m}\\
    w_a^{2,1} & w_a^{2,2}& \ldots &w_a^{1,m}\\
    \vdots & \ddots & \ldots &\vdots\\
    w_a^{\bar{n},1} & w_a^{\bar{n},2}& \ldots &w_a^{\bar{n},m}
  \end{bmatrix}.
\end{align*}
%
In compact form:
  \begin{align*}
    \bm{\Sigma}\mathbf{W}_a \approx  \mathbf{U}^{[d]},\qquad\text{with}
    % \hat{\mathbf{U}} \approx \mathbf{U}^{[d]}, 
  \end{align*}
  %
  $\mathbb{R}^{\eta\times\bar{n}}\ni \bm{\Sigma} = [\bm{\Sigma}_0,\bm{\Sigma}_1,\ldots,\bm{\Sigma}_{\eta -1}]^T$ with $\bm{\Sigma}_\kappa = \bm{\sigma}^T({\bf e}_{k+\kappa})$ and $\mathbb{R}^{\eta\times m}\ni {\bf U}^{[d]} = [{\bf U}_0,{\bf U}_1,\ldots, {\bf U}_{\eta-1}]^T$ with ${\bf U}_\kappa = \left({\bf u}_{a,\kappa}\right)^T$ for $\kappa = 0,1,\ldots,\eta-1.$

@@

 The neural network is validated by passing another subset of data that was not used for training purposes and comparing the output results of the neural network with the expected output results from the data set. An acceptable neural network model will meet the desired error requirements~\footnote{\hsize=0.9\textwidth \url{https://medium.com/autonomous-agents/bayesian-regularization-for-neuralnetworks-2f2d34f03adc}}.

@@

\todo[inline]{Need annotation of each of the pictures. Like that, we show what
  each of the equipment are}
\begin{figure}
    \centering
    \begin{subfigure}[b]{0.48\linewidth}
		\centering    		
    		\includegraphics[angle=270,width=0.9\linewidth]{figs/img/picturesVisitToAStuff/aStuffVisit2Nick}
    		\caption{}
    \end{subfigure}
    \begin{subfigure}[b]{0.48\linewidth}
		\centering    		
    		\includegraphics[angle=270,width=0.9\linewidth]{figs/img/picturesVisitToAStuff/hilMeasurementHannah}
    		\caption{}
    \end{subfigure}
    %\subfigure[b]{\includegraphics[width=0.48\linewidth]{figs/img/picturesVisitToAStuff/aStuffVisit2Nick}}
    %\subfigure[b]{\includegraphics[width=0.48\linewidth]{figs/img/picturesVisitToAStuff/hilMeasurementHannah}}
    \caption{Verifying voltage measurements on the HIL Bench}
    \label{fig:hilMeasuring}
\end{figure}
